Generating the Blueprints of the Java Ecosystem

### 2015-02-23 msr.tex
finalised authors
some changes / thoughts

\title{Generating the Blueprints of Java Ecosystem}

@@

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{cc}
   \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
  \centering
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
  \end{tabular}
}

@@

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature and some of them, like Chidamber and Kemerer~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} that have found their way in software development practice and tools.

@@

@@

The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}. The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.

In the literature, it is referred that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}. This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects. In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.

@@

The initial goal of this experiment was simply to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account. Build files or other resources that may contain {\sc dsl}s were not included. One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.

@@

The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}. Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements. In publication \cite{MKLGS14}, Mitropoulos et al. also experimented in a similar way, by running the findbugs~\cite{HP04} security and bugs audit tool on a large part of the maven repository. Our work differs from these these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.

>>>>

\title{Generating the Blueprints of the Java Ecosystem}

@@

\author{
  Vassilios Karakoidas\aueb \and Dimitris Mitropoulos\columbia \and Panos Louridas\aueb \and Georgios Gousios\run \and Diomidis Spinellis\aueb\\
  \begin{tabular}{c}
   \affaddr{\aueb Dept of Management Science and Technology}\\
   \affaddr{Athens University of Economics and Business}\\
   \affaddr{Athens, Greece}\\
   \email{\{bkarak,louridas,dds\}@aueb.gr}\\
  \end{tabular}
  \centering
  \begin{tabular}{cc}
   \affaddr{\run Department of Digital Security} & \affaddr{\columbia Computer Science Department}\\
   \affaddr{Radboud University Nijmegen} & \affaddr{Columbia University}\\
   \affaddr{Nijmegen, the Netherlands} & \affaddr{New York, United States}\\
   \email{georgios@cs.ru.nl} & \email{dimitro@cs.columbia.edu}\\
  \end{tabular}
}

@@

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artifacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics have appeared in the literature. Furthermore, some of them, like Chidamber and Kemerer's~\cite{CHKE94} and those presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools. % dimitro@bkarak: provide corresponding refs. Also you need to bulk this up. A paragraph referring to what we did. e.g "In this paper we present a dataset produced by applying three tools on all versions of a snapshot of the Maven repository. [...]".

@@

% dimitro@bkarak: This section *does not* present the dataset. It presents Maven. You should rename the section to "Dataset Construction Process" and merge it with the upcoming one. It should go like this: 1) We got this snapshot and 2) applied these three tools to create what you see in the next section. You'll present the experiment and *advertise* the effort.

@@

The Java platform exists for more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc sdk}. The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as Java Specification Requests ({\sc jsr}s), which are supported by prototype implementations.

In the literature, it is suggested that {\sc dsl}s are used to reduce software development cost, by introducing domain efficiency \cite{MHS05}. This thesis focuses on practical research aspects as well as with the theoretical ones; thus the first problem that needs to be examined, is to measure the adoption of {\sc dsl}s in software projects. In addition, the average number of {\sc dsl}s usually used in a software project needs to be investigated.

@@

The initial goal of this experiment was to provide quantifiable results that are indicative regarding the usage of each {\sc dsl}, thus only files containing Java code were taken into account. Build files or other resources that may contain {\sc dsl}s were not included. One final assumption was also made; if {\sc xpath} or {\sc xslt} were found in the source code, then the project would be marked that it also uses {\sc xml}, since those two languages are used for query and transformations on {\sc xml} {\sc dom} trees.

@@

The Maven ecosystem has been previously analyzed by Raemaekers et al.~\cite{RDV13} to produce the {\it Maven dependency dataset}. Apart from basic information like individual methods, classes, packages and lines of code for every {\sc jar}, this dataset also includes a database with all the connections between the aforementioned elements. In publication \cite{MKLGS14}, Mitropoulos et al. also experimented in a similar way, by running the FindBugs~\cite{HP04} tool on a large part of the maven repository. Our work differs from these two approaches since it presents the metrics calculated by the three aforementioned tools; \textit{ckjm}, \textit{jdepend}, and \textit{clmt}.
